---
title: "QPL Program Attendance"
author: "Matthew Magiera"
date: "2/28/2022"
output: pdf_document
---
```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```
Library and Data Loading
```{r}
setwd("~/QPL Projects/Project 2- LAMPS data")
library(tidyverse)
library(ggthemes)
library(readxl)
library(rio)
library(zoo)
library(writexl)
franny_list <- read_excel("psd_programs_franny.xlsx")
```

Merging spreadsheets into one

```{r}

df <- import_list("lamps_data_2020_present.xlsx", rbind = TRUE)
write_xlsx(df, "consolidated.xlsx")
```

Merging the two data sets using a left join.

```{r}
df <- left_join(franny_list, df)
```

Finding NA in the data frame.
```{r}

which(is.na(df), arr.ind = TRUE)
```

Removing row 3932 and making the Month column a date.
```{r}
df <- df %>%
  filter(!row_number() %in% 3932)

df$Month <- as.yearmon(df$Month, '%m/%Y')
df$Month <- as.Date(df$Month, format = "%m/%Y")
```

The # of programs and attendance of programs created by her staff
```{r}

bar_chart <- ggplot(data = df, aes(x = as.factor(`QPL Department`)))+
  geom_bar()+
  xlab("Programs")+
  ylab("Number of Programs")+
  ggtitle('Number of Programs Hosted by QPL Department') +
  theme_clean() 
  
bar_chart + coord_flip()

```

```{r}
bar_chart <- ggplot(data = df, aes(x = Attendance ,y = `QPL Department`))+
  geom_bar(stat = "identity") +
  ggtitle("Attendence For Each QPL Department")+
  theme_clean()
bar_chart + coord_flip()
```



Which programs are missing attendance (or have a 0 in the "Attendance" column)?

Filter data frame where attendance is Zero
```{r}
df_zero <- df %>%
  group_by(`QPL Department`) %>%
  summarise(Attendance = n(), .groups = 'drop')


```

```{r}
bar_chart <- ggplot(data = df_zero, aes(x = as.factor(`Staff Name`)))+
  geom_bar() +
  xlab("Employee Names") +
  ylab("Number of Programs") +
  ggtitle("Employee Hosted When The Attendance Is Zero") +
  theme_clean()
bar_chart + coord_flip()
```
```{r}
bar_chart <- ggplot(data = df_zero, aes(x = as.factor(`QPL Department`)))+
  geom_bar() +
  xlab("Program Names") +
  ylab("Number of Programs")+
  ggtitle("Programs Where The Attendance Is Zero")+
  theme_clean()
bar_chart + coord_flip()
```
Which staff hosted the most # of programs? Which staff had the most attended programs?

```{r}
bar_chart <- ggplot(data = df, aes(x = as.factor(`Staff Name`)))+
  geom_bar() +
  xlab("Employee Names") +
  ylab("Number of Programs") +
  ggtitle("Employee Hosted the Number of Programs ") +
  theme_clean()
bar_chart + coord_flip()
```

```{r}
bar_chart <- ggplot(data = df, aes(x = as.factor(`Staff Name`), y = Attendance))+
  geom_bar(stat = "identity")+
  xlab("Employee Names") +
  ylab("Attendance") +
  ggtitle("Employee By Attendance ") +
  theme_clean()
bar_chart + coord_flip()
```

Top 10 Most Attended Programs
```{r}
df <- df[with(df, order(-Attendance)),]
df <- df[1:10,]
print(df)
```
```{r}
non_zero <- df %>%
  filter(Attendance != 0)
```

```{r}
library(lubridate)
non_zero %>%
  mutate(Month = ym(Month))
  ggplot(aes(x = Month, y = Attendance)) +
  geom_line()+
  scale_x_date(date_labels = "%b %Y", date_breaks = "1 month")
```

